Rising from the Ashes: How the Milky Way Got Its Scars

### 2024-05-02 paper/src/met.tex
Add res levels to methods

>>>>

We used a mass resolution of $6\times10^4\,\Msun$ for the gas and $3\times10^5\,\Msun$ for the dark matter. This is closest to a resolution of level 4 in the AURIGA simulations \citep{2017MNRAS.467..179G}, and is about $0.7\times$ the mass resolution of TNG50-1 \citep{2019MNRAS.490.3234N,2019MNRAS.490.3196P}. All collisionless particles have a fixed softening length of $40\,\pc$. The gas has a softening length $2.5\times$ the cell size, with a minimum size of $10\,\pc$. Snapshots were saved at intervals of $0.025\,\Gyr$.
